\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}
\usepackage{hyperref}

\begin{document}

\begin{flushright}
Satya Karan \\
Müngersdorfer Str. 47 \\
12524 Berlin, Germany \\
\href{mailto:satyabratadevops23@gmail.com}{satyabratadevops23@gmail.com} \\
+49 15211796270 \\
\href{https://www.linkedin.com/in/satya-karan}{linkedin.com/in/satya-karan}
\end{flushright}

\vspace{1em}

\textbf{Hiring Manager} \\
[Navigating.art] \\
[Berlin] \\

\vspace{1em}

\textbf{Subject: Application for AWS DevOps Engineer Position}

Dear Hiring Manager,

I am writing to express my interest in the Senior DevOps Engineer position at Navigating.art, as advertised. With 5+ years in DevOps and 7 years in backend development using Perl and Python - I bring a strong combination of infrastructure automation, AWS cloud expertise, and production support that aligns well with your needs.

In my most recent role at Quicken Software, I managed CI/CD pipelines using Jenkins and Docker, orchestrated containers with Kubernetes, and automated infrastructure with Terraform and Ansible. I have extensive experience in AWS, having worked with services such as EC2, VPC, ELB, ECS, and S3. At Nomis Solutions, I was recognized as the Top Performer in Q2 2024 for my contributions to Tableau automation and successfully optimized deployments, reducing release time by 50\%.

What sets me apart is my ability to not only implement scalable DevOps solutions but also mentor junior team members and collaborate across agile teams to meet sprint goals. I am proficient in monitoring tools such as Datadog and Splunk, and I have hands-on experience handling production incidents, container-level troubleshooting, and ensuring high availability of services.

Currently based in Berlin on a Chancenkarte Visa (valid until November 2025), I am available for immediate employment. I am excited about the opportunity to bring my skills to an innovative team and contribute to your Company's ongoing success in delivering high-quality, reliable cloud infrastructure and deployment process.

Thank you for considering my application. I would welcome the opportunity to further discuss how I can add value to your team.


Sincerely, 

\textbf{Satya Karan}

\end{document}