
\documentclass[11pt,a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{parskip}

\titleformat{\section}{\large\bfseries}{}{0em}{}

\begin{document}


\begin{itemize}[leftmargin=*]
{\LARGE \textbf{Mr. S. Ganeswar Karan}} \\
Hainstrasse, Berlin 12524, Germany \\
\texttt{Handy: +49 (0)15211796270} \\
\texttt{Email: satyakaran2020@gmail.com} \\
\href{https://www.linkedin.com/in/skaran-developer/}{linkedin.com/in/skaran-developer} \\
\href{https://github.com/satyakaibm/MyResume/tree/master/Perl_Developer}{github.com/satyakaibm/MyResume} \\
\texttt{Visum: Deautschland Chancenkarte Visa (bis November 2025)}  \\
\texttt{Available: Immediate | Relocation: Open all across Germany} \\
\end{center}

\section*{Professional Summary}
\textbf{Total 11 years of experience} in Backend Development, including Cloud and DevOps practices. \textbf{Relevant 7 years in Perl Backend Development}, and 4 years in Python Backend Development. Also, skilled in CI/CD pipeline, Docker containerization and basic knowledge of Kubernetes orchestration, infrastructure automation using Terraform for AWS cloud services. Adopted handling the production issues, mentoring the team member, and working in Agile environments. 

\section*{Technical Skills}
\textbf{Languages \& Framework \& Scripting:} Perl, CPAN, Mojolicious,  Bash \\
\textbf{Cloud \& DevOps:} AWS, Jenkins, Git, Bitbucket \\
\textbf{Containers \& IaC:} Docker, Ansible \\
\textbf{Monitoring Tools:} Datadog, Splunk, Nagios \\
\textbf{Databases:} MySQL, Oracle \\
\textbf{OS:} Linux (RHEL, Ubuntu), Windows OS

\section*{Experience}

\textbf{Senior Software Engineer} \hfill Quicken Software (Aug 24 – Apr 25) \\
\begin{itemize}[leftmargin=*]
  \item Developed the app using Perl Web framework mojolicious with REST API to get and post the backend data for processing. 
  \item Developed RESTFUL Web Services and with microservice architecture.
  \item Generated documentation for Perl packages and unit testing. 
  \item Designed and optimized relational database models and schemas using DBI and DBD modules.
  \item Managed CI/CD pipelines in Jenkins and automated infrastructure using Bash Shell.
  \item Worked with AWS services including EC2, ECS, VPC, and Load Balancers.
  \item Writing and managing the Dockerfile for building the Docker images and managing the containers.
  \item Conducted health checkup or sanity checkup of portfolio for different strategies.
  \item Monitored production application system high availability and on-call support, answering the calls and tickets.
  \item Fixed the application Production issues which are integrated with different DevOps processes.
\end{itemize}

\vspace{1em}
\textbf{Senior System Engineer} \hfill Nomis Solutions (Oct 23 – Jul 24) \\
\begin{itemize}[leftmargin=*]
  \item Automated cloud infrastructure using Terraform and managed clusters.
  \item Focused on Agile methodologies and participated in sprint planning and Scrum meetings. 
  \item Reduced the Perl backend application deployment time by 50\% via optimized Jenkins and Docker pipelines.
  \item Recognized as Top Performer in Q2 2024 for process automation.
\end{itemize}

\vspace{1em}

\textbf{Senior Backend Engineer} \hfill Smatbee Network (Oct 2020 – Oct 2023) \\
\begin{itemize}[leftmargin=*]
  \item Designed and implemented CI/CD pipelines using Jenkins, Docker, and Ansible.
  \item Created AWS resources including S3, EC2, VPC, and Auto Scaling.
  \item Deploying cloud infrastructure services in AWS cloud using Terraform.
  \item Mentored junior developers and worked in Agile sprints.
\end{itemize}

\vspace{1em}

\textbf{Senior Software Engineer} \hfill Xoriant Solutions (Aug 2019 – Oct 2020) \\
\begin{itemize}[leftmargin=*]
  \item Written clean, efficient, and scalable code using Python and FLASK framework.  
  \item Taken care of CI/CD pipeline projects using Teamcity tool.
  \item Fixed the ongoing Production issues and root cause analysis. 
  \item Tried the manual task to Automate using Shell script, and Python. 
\end{itemize}

\section*{Education}
\textbf{Bachelor of Technology – Computer Science and Engineering} \\
Biju Patnaik University of Technology, Rourkela, India (2009)

\section*{Certifications}
\begin{itemize}[leftmargin=*]
  \item Red Hat Certified System Administrator (RHCSA) 
  \item Python using AI from TechSchool 
\end{itemize}

\section*{Achievements}
\begin{itemize}[leftmargin=*]
  \item Reduced deployment time by 50\% via optimized CI/CD at Smatbee Network. 
  \item Awarded Top Performer in Q2 2024 at Nomis Solutions for Application automation 
\end{itemize}

\section*{GitHub Projects}
\begin{itemize}[leftmargin=*]
  \item \href{https://github.com/satyakaibm/jenkins-resources.git}{CI/CD Pipeline}  \\
  \item \href{https://github.com/satyakaibm/Ansible_practice.git}{Ansible Automation} 
\end{itemize}

\end{document}

